Biostatistician, data analyst, and SAS developer. Specialize in conducting large registry-based observational studies and post-marketing safety studies. Extensive experience in statistical modeling in SAS, including developing SAS macros and SAS/IML programs.\\

\section{Professional Experience}

\begin{entrylist}
  \entry
    {Since 2018}
    {Senior Biostatistician - Cell Therapy Lead}
    {Milwaukee, WI}
    {
      \textit{Center for International Blood and Marrow Transplant Research \\ Medical College of Wisconsin}
      % \vspace{-\baselineskip}
      \begin{itemize}
        \item Served as the Lead Biostatistician of the Cellular Therapy Functional Area, responsible for overseeing and managing study portfolio for both working committee and corporate studies.
        \item Provided statistical support and consultancy for multiple PASS studies of commercial CAR T-cell products in collaboration with lead pharmaceutical companies. Prepared SAPs, data summary reports, and annual statistical reports for FDA submissions.
        \item Oversaw the data retrieving process for the Cellular Therapy Data Registry. Ensured data integrity across multiple stages of data transition from Oracle database to SAS data extract.
        \item Provided supervision to entry-level statisticians, responsible for administrative functions such as hiring, mentoring, and managing workflows of statistical staffs.
      \end{itemize}
    }
  \entry
    {2011-2018}
    {Biostatistician}
    {Milwaukee, WI}
    {
      \textit{Center for International Blood and Marrow Transplant Research \\ Medical College of Wisconsin}
      % \vspace{-\baselineskip}
      \begin{itemize}
        \item Conducted advanced statistical analyses for 2-3 research projects each year, including developing SAS and R programs, describing data, testing hypotheses, selecting models and interpreting results.
        \item Administered 5-10 research projects each year with close collaboration with principle investigators across the country. Ensured their successful publications on high impact scientific journals, such as \textit{New England Journal of Medicine}, \textit{Journal of Clinical Oncology}, and \textit{Blood}.
        \item Served as the developer and maintainer of the internal SAS code repository.
        \item Provided training and consultancy to entry-level statisticians.
      \end{itemize}
    }
  \entry
    {2009-2011}
    {Epidemiologist Intern}
    {St. Paul, MN}
    {
      \textit{Division of Health Promotion and Chronic Disease \\ Minnesota Department of Health}
      % \vspace{-\baselineskip}
      \begin{itemize}
        \item Conducted statistical analyses in SAS for the survey data of \textit{I Can Prevent Diabetes} program to evaluate its effectiveness.
        \item Prepared data for multiple scientific reports for successful grant applications and conference presentations.
      \end{itemize}
    }
\end{entrylist}

\section{Education}

\begin{entrylist}
%   \entry
%     {2018}
%     {Medical College of Wisconsin}
%     {Milwaukee, WI}
%     {Courseworks: applied survival analysis}
  \entry
    {2008-2010}
    {M.P.H. in Epidemiology}
    {Minneapolis, MN}
    {
      \textit{University of Minnesota, Twin Cities}
      % \vspace{-\baselineskip}
      \begin{itemize}
        \item Major courseworks: statistical inference, generalized linear model, mixed model, survival analysis, epidemiological method, SAS and R programming, pathophysiology
        \item Thesis: \textit{Role of selection bias in pancreatic cancer case-control studies}
      \end{itemize}
    }
  \entry
    {2004–2008}
    {B.S. in Biological Science}
    {Shanghai, China}
    {
      \textit{Fudan University}
      % \vspace{-\baselineskip}
      \begin{itemize}
        \item Major courseworks: immunology, genetics, biochemistry, physiology, neuroscience
      \end{itemize}
    }
\end{entrylist}
